---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# ganttrify

<!-- badges: start -->
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://www.tidyverse.org/lifecycle/#experimental)
<!-- badges: end -->

`ganttrify` facilitates the creation of nice-looking Gantt charts, commonly used in project proposals and project management.

## Motivation

It is possible to find online documented attempts at facilitating the creation of Gantt charts from R. Some of them (e.g. [this](https://www.molecularecologist.com/2019/01/simple-gantt-charts-in-r-with-ggplot2-and-the-tidyverse/) and [this](https://davetang.org/muse/2017/02/03/gantt-chart-using-r/)) use 'ggplot2', but I feel they do not look very nice. The same goes for the answers I found in the [relevant Stackoverflow question](https://stackoverflow.com/questions/3550341/gantt-charts-with-r).


Even [Plotly](https://moderndata.plot.ly/gantt-charts-in-r-using-plotly/) enables the creation of Gantt charts in R, but again, I don't like the end result. 

I did find a [solution that was rather visually satisfying](https://insileco.github.io/2017/09/20/gantt-charts-in-r/), but it was in base R, and all the cool kids nowadays know that base plotting in R exists only [for compatibility with S](https://twitter.com/whydoesr): not an option! (Hey, I'm joking, don't @ me!)

Given what is evidently my posh taste for Gantt charts, I had no other option than making this package with a pretentious, gentrified name, instead of the obvious "ganttr". 

Please welcome `ganttrify`.

## Disclaimer

More seriously, this has been a quick attempt at making decent-looking Gantt charts. They are really not that beautiful (yet).

And yes, I will enable all the customisations you like, but first I actually need to submit this project.

## Features

Take an adequately formatted spreadsheet and turn it into a Gantt chart made with ggplot2.

## Future features

- further customisation and more options
- shiny app to facilitate creation and editing of Gantt charts for non-R users

## Installation

You can install the development version from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("giocomai/ganttrify")
```

## Example

Here is an example project:

```{r echo=FALSE}
knitr::kable(ganttrify::test_project)
```


Month since the beginning of the project are used as reference in order to make it easier to change the date when the project starts without needing to change the timing of all activities.



```{r gantt_chart}
library("ganttrify")

ganttrify(df = ganttrify::test_project, start_date = "2020-03")
```


"But what if I wanted to add spot labels for events, deliverables, outputs, milestones, things like that?", you asked.

Just put them in a table with these column names, and you will be served.

```{r echo=FALSE}
knitr::kable(ganttrify::test_spots)
```

```{r gantt_charts_with_events}
ganttrify(df = ganttrify::test_project,
          spots = ganttrify::test_spots,
          start_date = "2020-03")
```

"I can't read the text, can I change the text size?", I heard. 
"Also, is it possible to outline quarters?"

You're welcome. 

```{r gantt_charts_resized_text}
ganttrify(df = ganttrify::test_project,
          spots = ganttrify::test_spots,
          start_date = "2020-03",
          size_text_relative = 1.2, 
          mark_quarters = TRUE)
```